Catchy Title Goes Here

### 2018-06-14 Paper/paper.tex
minor changes

\subsection{Data \label{subsec:Data}}

@@

Figure~\ref{fig:simplots} shows the injected (dashed lines) and recovered (solid (purple or orange) lines) curves for the force of infection and vaccination hazard from simulated data with vaccine efficacy of $\gamma = 0.9$ (orange) and $\gamma = 0.6$ (indigo). The top panel shows the force of infection, and it is very clear from this panel that a Weibull distribution is not a good fit for the true force of infection, which is bimodal.  Because of this, we do not expect to be able to accurately infer the simulation parameters (i.e., $\gamma$). We examine the inferred values for this parameter in Figure~\ref{fig:veffsimdata}.

\begin{figure*}
\includegraphics[width=\textwidth,angle=0]{figures/SimPlots-crop.pdf}
\caption{caption\label{fig:simplots}}
\end{figure*}

This Figure shows the posterior distributions and assumed values for $\gamma$ from simulated datasets with four different values of $\gamma$. The top panel is generated by analyzing all three datasets, and the bottom panel using only case and vaccination data. In addition to the assumed values and the posteriors, we also show the prior on $\gamma$ as a yellow line. In the top panel we see, as expected, that the inferred values for $\gamma$ are systematically biased away from the injected values - they turn out to be consistently biased low in this case. Although this means that we do not necessarily infer an accurate value for vaccine efficacy with this data using this model, it is worth noting that we do infer the correct \emph{ordering} for $\gamma$. That is, if these were four different locations, we would correctly identify the location with the lowest vaccine efficacy.

@@

\subsection{DRC Data \label{subsec:DRC}}
\begin{figure*}
\includegraphics[width=\textwidth,angle=0]{figures/VaccFOIveff-crop.pdf}
\caption{caption\label{fig:foivaccveff}}
\end{figure*}

\subsection{DRC Data \label{subsec:DRC}}
\begin{figure*}
\includegraphics[width=\textwidth,angle=0]{figures/SeroPlots-crop.pdf}
\caption{caption\label{fig:sero}}
\end{figure*}
Application to the DRC data
	Pairs plots for all provinces ? compare for fits with only case data to fits with case+serology ? discuss any appearance of non-identifiability (?? What is non-identifiability?)	
Figure 2 ? pairs plots for all provinces and two models

Figure 3 ? Fitted seroprevalence curves for all provinces (maintain province color scheme throughout all figures). Note that x-scale should be years (up to 20 at least), it doesn?t make much sense over 59m
	- could probably squeeze all 11 into a single figure if played out well

Figure 4 ? fitted hazard functions illustrating variation in vaccination and force of infection.  4-panel, vaccination and FOI hazards for fits with and without serology data. (Note that FOI hazard should be on an x-scale of years, it doesn?t make much sense over 59m)
	- discuss variation observed.  Where is vaccination timely, where is FOI highest

Figure 5 ? comparison of prioritization
	- maybe 2 panels showing the seroprevalence by X years and the estimated vaccine efficacy for case data only v. case plus serology data.

	ASIDE ? would be worth plotting something like maximum vaccination coverage vs. some summary measure of the FOI ? you would expect to see lower FOI in places with higher coverage. If this pattern exists, that would definitely be worth showing!  There might be other summaries of the vaccination hazard that are more informative ? e.g. that account for speed up uptake AND max coverage.

>>>>

\subsection{Data \label{subsec:Data}}
Description of the data.

@@

Figure~\ref{fig:simplots} shows the injected (dashed lines) and recovered (solid (purple or orange) lines) curves for the force of infection and vaccination hazard from simulated data with vaccine efficacy of $\gamma = 0.9$ (orange) and $\gamma = 0.6$ (indigo). The top panel shows the force of infection, and it is very clear from this panel that a Weibull distribution is not a good fit for the true force of infection, which is bimodal.  Because of this, we do not expect to be able to accurately infer the simulation parameters (i.e., $\gamma$). We examine the inferred values for this parameter in Figure~\ref{fig:simplots}.

\begin{figure*}
\includegraphics[width=0.9\textwidth,angle=0]{figures/SimPlots-crop.pdf}
\caption{\label{fig:simplots} Results from study using simulated data. 
The top left plot shows the posterior distributions for each of four different datasets generated with four different vaccine effectiveness ($\gamma$). The injected values are shown as dashed lines, and the recovered distributions are labelled with the associated value of $\gamma$. The prior is shown as a solid yellow line. The top panel of this plot is generated using all three datasets, and the bottom panel uses only vaccination and serology data. We find that the recovered value of $\gamma$ is typically biased low, but that the ordering of datasets by $\gamma$ is recovered correctly. In the cases of high $\gamma$ and no serology data, the recovered posteriors are dominated by the prior.
The top right plot shows the injected (dashed) and recovered (solid) force of infection (top panel) and vaccination hazard (bottom panel) for the same four datasets. The Weibull is not a good fit to the injected foi, but the resulting fits to the observable data (bottom plot) are not overly biased. The fit to the vaccination hazard is similarly not perfect, and the overly-high peaks can explain the general biasing of $\gamma$ to low values. 
The bottom plot shows the injected (points) data and recovered (lines) curves for the highest (orange) and lowest (indigo) values of $\gamma$ for seroprevalence data (top), vaccination data (middle), and case data (bottom).}
\end{figure*}

This figure shows the posterior distributions and assumed values for $\gamma$ from simulated datasets with four different values of $\gamma$. The top panel is generated by analyzing all three datasets, and the bottom panel using only case and vaccination data. In addition to the assumed values and the posteriors, we also show the prior on $\gamma$ as a yellow line. In the top panel we see, as expected, that the inferred values for $\gamma$ are systematically biased away from the injected values - they turn out to be consistently biased low in this case. Although this means that we do not necessarily infer an accurate value for vaccine efficacy with this data using this model, it is worth noting that we do infer the correct \emph{ordering} for $\gamma$. That is, if these were four different locations, we would correctly identify the location with the lowest vaccine efficacy.

@@

\subsection{Application to DRC Data \label{subsec:DRC}}
\begin{figure*}
\includegraphics[width=0.85\textwidth,angle=0]{figures/SeroPlots-crop.pdf}
\caption{caption\label{fig:sero}}
\end{figure*}
\begin{figure*}
\includegraphics[width=\textwidth,angle=0]{figures/VaccFOIveff-crop.pdf}
\caption{caption\label{fig:foivaccveff}}
\end{figure*}
\begin{figure}
\includegraphics[width=\columnwidth,angle=0]{figures/RiskRank-crop.pdf}
\caption{caption\label{fig:riskrank}}
\end{figure}
